Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-12-02 doc/om-paper/paper.tex
unpushed changes to paper.

@@

@@

@@

\begin{figure}
  \centering
  \begin{tabular}{p{3cm}|p{3cm}|l|l|}
                                  & Modules modified    & Lemmas modified & Lemma classes modified\\
  \hline \hline
  Byzantine-only fault model      & 0                   & 0               & 0 \\
  \hline
  Time-triggered message-passing  & \texttt{clock}, \texttt{relay}
                                  , \texttt{receiver}   & 0               & 0 \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications.}
  \label{fig:effort}
\end{figure}
To demonstrate the modularity of the model and verification approach, in this section, we explore variants to the model and discover the effort required to implement the modifications and repair the proofs. The results are summarized in Figure~\ref{sec:effort} and sketched below.

\paragraph{Fault model.}
Modifying the fault model is easy. In involves modifying the definition of a single function, \texttt{mfa}, that takes as an argument the static assignment of node identifiers to faults. Moreover

\paragraph{Time-triggered messaging.}

>>>>

\lee{grep to get consistent manifest/benign, also lieutenant vs relay/receiver.}

@@

\lee{what we have defined are actually strictly stronger than synchronous observers since they can modify state.}

@@

\lee{cite abstractions paper and point out that we can model faults on transmission rather than node}

@@

\begin{figure}
  \centering
  \begin{tabular}{|p{3cm}|p{3cm}|l|l|}
  \hline
                                  & Transition systems & Definitions & Invariants & Invariant classes \\
  \hline \hline
  Omissive-asymetric faults       & 0                   & 4          & 2          & 1                 \\
  \hline
  Time-triggered messaging        & 3                   & \lee{todo} & 0          &                   \\
  Mid-value selection             &\lee{todo}           &  \lee{todo}&\lee{todo}  & \lee{todo}        \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications.}
  \label{fig:effort}
\end{figure}
To demonstrate the modularity of the model and verification approach, in this section, we explore variants to the model and report the effort required to implement the modifications and repair the proofs. The results are summarized in Figure~\ref{sec:effort} and sketched below. In the table, for each modification, we report how much of the model must be modified. Specifically, we report on the number of synchronously-composed transition systems, function definitions, invariants, and invariants classes (as defined in Section~\ref{sec:invariants}) that must be modified.

\paragraph{Omissive asymetric faults.}
Remove faults already described by the fault model is easy. Recall that in our model faults do not appear in the system specification and only operate on the calendar. Removing a fault from the system requires only setting the number of a particular kind of faults to zero in the maximum fault assumption.

Adding new kinds of faults requires more work but is modular. Consider adding \emph{omissive asymmetric faults}, a restriction of Byzantine faults in which a broadcaster either sends the correct value or a manifest fault~\cite{}, to the fault model. Doing so requires modifying none of transition systems. However, we modify four definitions (\texttt{msg()}, characterizing the result on the calendar due to a faulty message; \texttt{omissive_asymmetric_fault_constraint()}, defining the fault, and two functions that characterize the overall maximum fault assumption). Two invariants, both in the class of invariants cover faults, are extended to cover the cases where a sender is omissive asymmetric.

\paragraph{Time-triggered messaging.}
Oral Messages and its variants are synchronous protocols, in which communication occurs in rounds. In our original model, the nodes do not explicitly depend on a clock.

\lee{todo}

\paragraph{Mid-value selection.}

\lee{todo}

\lee{any other modifications?}
